Tables

### 2021-08-02 analysis/benchmarks.Rmd
refactor: move common yaml headers into _site.yml
fix: working directory for targets

---
title: "Benchmarks"
output:
  workflowr::wflow_html:
    toc: true
    fig.width: 12
    fig.height: 8
editor_options:
  chunk_output_type: console
---

```{r benchmarks_setup, message = FALSE}
library("targets")
library("mlr3viz")
library("viridis")
library("ggplot2")
tar_load(bmrk_results)
```

>>>>

---
title: "Benchmarks"
output:
  bookdown::html_document2:
    fig.width: 12
    fig.height: 8
---

```{r benchmarks_setup, message = FALSE}
library("targets")
library("mlr3viz")
library("viridis")
library("ggplot2")

withr::with_dir(rprojroot::find_rstudio_root_file(), {
    tar_load(bmrk_results)
})
```

### 2021-08-02 analysis/boxplots.Rmd
refactor: move common yaml headers into _site.yml
fix: working directory for targets

---
title: "Boxplots"
output:
  workflowr::wflow_html:
    toc: true
editor_options:
  chunk_output_type: console
---

```{r boxplots_setup, message = FALSE}
library("targets")
library("beeswarm")
library("viridisLite")
tar_load(imp_data)
tar_load(zlog_data)

>>>>

---
title: "Boxplots"
---

```{r boxplots_setup, message = FALSE}
library("targets")
library("beeswarm")
library("viridisLite")

withr::with_dir(rprojroot::find_rstudio_root_file(), {
    tar_load(imp_data)
    tar_load(zlog_data)
})

### 2021-08-02 analysis/corrplot.Rmd
fix: suppress package startup messages
fix: working directory for targets

---
title: "Corrplot"
output:
  workflowr::wflow_html:
    toc: true
    fig.width: 12
    fig.height: 12
editor_options:
  chunk_output_type: console
---

```{r corrplot_setup}
library("corrplot")
library("targets")
tar_load(imp_data)
```

>>>>

---
title: "Corrplot"
output:
  bookdown::html_document2:
    fig.width: 12
    fig.height: 12
---

```{r corrplot_setup, message = FALSE}
library("corrplot")
library("targets")

withr::with_dir(rprojroot::find_rstudio_root_file(), {
    tar_load(imp_data)
})
```

### 2021-08-02 analysis/histograms.Rmd
fix: working directory for targets

---
title: "Histograms"
output:
  workflowr::wflow_html:
    toc: true
editor_options:
  chunk_output_type: console
---

```{r histograms_setup, message = FALSE}
library("targets")
tar_load(imp_data)
tar_load(zlog_data)

>>>>

---
title: "Histograms"
---

```{r histograms_setup, message = FALSE}
library("targets")

withr::with_dir(rprojroot::find_rstudio_root_file(), {
    tar_load(imp_data)
    tar_load(zlog_data)
})

### 2021-08-02 analysis/linecharts.Rmd
refactor: move common yaml headers into _site.yml
fix: working directory for targets

---
title: "Linecharts"
output:
  workflowr::wflow_html:
    toc: true
    fig.width: 12
    fig.height: 8
editor_options:
  chunk_output_type: console
---

```{r linecharts_setup, message = FALSE}
library("targets")
tar_load(zlog_data)
```

>>>>

---
title: "Linecharts"
output:
  bookdown::html_document2:
    fig.width: 12
    fig.height: 8
---

```{r linecharts_setup, message = FALSE}
library("targets")

withr::with_dir(rprojroot::find_rstudio_root_file(), {
    tar_load(zlog_data)
})
```

### 2021-08-02 analysis/missing.Rmd
fix: load missing ameld package
fix: working directory for targets

---
title: "Missing Data"
output:
  workflowr::wflow_html:
    toc: true
    fig.width: 10
    fig.height: 10
editor_options:
  chunk_output_type: console
---

```{r missing_setup}
library("targets")
tar_load(raw_data)

>>>>

---
title: "Missing Data"
output:
  bookdown::html_document2:
    fig.width: 10
    fig.height: 10
---

```{r missing_setup}
library("targets")
library("ameld")

withr::with_dir(rprojroot::find_rstudio_root_file(), {
    tar_load(raw_data)
})

### 2021-08-02 analysis/survivalplots.Rmd
fix: working directory for targets

---
title: "Survival Plots"
output:
  workflowr::wflow_html:
    toc: true
    fig.width: 12
    fig.height: 8
editor_options:
  chunk_output_type: console
---

```{r survplots_setup, message = FALSE}
library("targets")
library("ameld")
library("survival")
tar_load(zlog_data)

>>>>

---
title: "Survival Plots"
output:
  bookdown::html_document2:
    fig.width: 12
    fig.height: 8
---

```{r survplots_setup, message = FALSE}
library("targets")
library("ameld")
library("survival")

withr::with_dir(rprojroot::find_rstudio_root_file(), {
    tar_load(zlog_data)
})

### 2021-08-02 analysis/tables.Rmd
fix: working directory for targets

---
title: "Tables"
output:
  workflowr::wflow_html:
    toc: true
editor_options:
  chunk_output_type: console
---

```{r histograms_setup, message = FALSE}
library("targets")
library("skimr")
tar_load(raw_data)
tar_load(imp_data)
tar_load(zlog_data)
```

>>>>

---
title: "Tables"
---

```{r histograms_setup, message = FALSE}
library("targets")
library("skimr")

withr::with_dir(rprojroot::find_rstudio_root_file(), {
    tar_load(raw_data)
    tar_load(imp_data)
    tar_load(zlog_data)
})
```
